Topic Modeling of News

### 2018-02-08 paper/R/02_cleanAndCombine.Rmd
delete articles about DB

  # remove articles about the weater
  filter(!grepl("wetter", url))
```

@@

## Preparation
```{r}
btw <- btw %>% 
  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
```

@@

### without stemming
processed1 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out_ownership <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
out_ownership$meta$ownership <- as.factor(out_ownership$meta$ownership)
###

@@

save(btw, out_ownership, file="../output/btw_comb_ownership.Rda")
```

>>>>

  # remove articles about the weater
  filter(!grepl("wetter", url)) %>%
  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
```

@@

## Preparation
```{r}
btw <- btw %>% 
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
```

@@

### without stemming
processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
out$meta$ownership <- as.factor(out$meta$ownership)
###

@@

save(btw, out, file="../output/btw_comb.Rda")
```
